An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-01-28 preprint/positive_results_SRs_RRs.Rmd
tiny text change

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world. 
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability. 
But when published findings are systematically biased, cumulative science breaks down: 
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct. 
For more than half a century, scientists have repeatedly noticed a suspiciously high "success" rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that a whopping $97.28\%$ of the studies that used significance tests rejected the null hypothesis. 
A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study. 
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$. 
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.

>>>>

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world. 
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability. 
But when published findings are systematically biased, cumulative science breaks down: 
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct. 
For more than half a century, scientists have repeatedly noticed a suspiciously high "success" rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of the studies that used significance tests rejected the null hypothesis. 
A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study. 
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$. 
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.

### 2020-01-28 preprint/positive_results_SRs_RRs.tex
tiny text change

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.

>>>>

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.
